Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2023-12-19 paper.tex
Replace 'width 7' with 'width 7 pixels'

\section{Edge detection filter}
\label{sec:filter}
For edge detection we use a kernel with the width 7 with coefficients inversely
proportional to distance to kernel's central element. The central element has
such value, so all elements of the kernel sum to zero:
\begin{equation}
  E_k = S \left\{
  \begin{array}{ll}
    -\sum\limits_{\substack{l \\ l \ne 0}} E_l & \quad k = 0 \\
    1 / \rho(k, 0) & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation}
For 3D case $S=172.96$ and for 2D case $S=30.46$ \cite{postnicov20232}.

>>>>

\section{Edge detection filter}
\label{sec:filter}
For edge detection we use a kernel with the width 7 pixels with coefficients
inversely proportional to distance to acentral element of the kernel. The
central element is determined by a property that all elements of the kernel sum
to zero:
\begin{equation}
  E_k = S \left\{
  \begin{array}{ll}
    -\sum\limits_{\substack{l \\ l \ne 0}} E_l & \quad k = 0 \\
    1 / \rho(k, 0) & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation}
For 3D case $S=172.96$ and for 2D case $S=30.46$ \cite{postnicov20232}.
